---
title: "MAPR02"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prerequisites

### Equipment and software requirements

Attendees are expected to use have a working version of R (version 4.0 or higher) and RStudio (version 1.4 or higher) installed.

R and RStudio are supported by PC, Linux, and MacOS and can be downloaded for free by following these links
http://www.r-project.org/ and https://www.rstudio.com/products/rstudio/download/#download.

### R packages

Run the code below in R to install all of the required R packages.

```{r, eval=FALSE}
install.packages("remotes")
remotes::install_github("geocompr/geocompkg")
install.packages("terra")
```

### Check if it works

Afterwards, run the code below (you should see the map as a result):

```{r}
library(tmap)
library(spData)
library(spDataLarge)
library(terra)
nz_elev = rast(nz_elev)
tm_shape(nz_elev) +
  tm_graticules() +
  tm_raster() +
  tm_shape(nz) +
  tm_borders()
```

Please see https://datacarpentry.org/geospatial-workshop/setup.html for instructions on how to install geospatial library dependencies.
